A Decision Procedure for (Co)datatypes in SMT Solvers

### 2015-02-17 tex/body.tex
more

In the following, we consider only normal models.
When constructing a model $\M$ for $\Ec$,
it remains only to specify how $\M$ interprets wrongly applied selector terms and variables.
For the latter, this will be based on the mapping $\Val$ computed in phase~2 of the calculus.

@@

Intuitively, this lemma states three properties of $\ValC$ that ensure a normal
model $\M$ can be trivially constructed for $\Ec$. Part~\PART{1} states that the
values in the range of $\ValC$ are $\alpha$-equivalent to a value in normal
model. In particular, this means they are closed, normal, and acyclic when
required. Part~\PART{2} states that the interpretation of all subterms in the
range of $\ValC$ depends on its associated variable only. In other words, the
interpretation of a subterm $t$ where $\muvar(t) = {\Varec{x}}$ is equal to
$\ValC \ec{x}$, independently of the context in which it is interpreted.
Part~\PART{3} states that $\ValC$ is injective, which in the following ensures
that a distinct values can be associated with each equivalence class in a
corresponding model.

>>>>

In the following, we consider only normal models.
When constructing a model $\M$ for $\Ec$,
it remains only to specify how $\M$ interprets wrongly applied selector terms and variables.%
\rem{Variables are really part of the model then?}
For the latter, this will be based on the mapping $\Val$ computed in phase~2 of the calculus.

@@

Intuitively, this lemma states three properties of $\ValC$ that ensure a normal
model $\M$ can be trivially constructed for $\Ec$. Property~\PART{1} states that the
values in the range of $\ValC$ are $\alpha$-equivalent to a value in normal
model. In particular, this means they are closed, normal, and acyclic when
required. Property~\PART{2} states that the interpretation of all subterms in the
range of $\ValC$ depends on its associated variable only. In other words, the
interpretation of a subterm $t$ where $\muvar(t) = {\Varec{x}}$ is equal to
$\ValC \ec{x}$, independently of the context in which it is interpreted.
Property~\PART{3} states that $\ValC$ is injective (modulo
$\alpha$-equivalence), which in the following ensures that a distinct value can
be associated with each equivalence class in a corresponding model.
